---
title: 'Code Stroke Analysis Dashboard'
author: "Implementation by [Juan González García](mailto:jgonzalezgarc.iacs@aragon.es)"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    self_contained: yes
---

  <!-- html_document: -->
  <!--   toc: true -->
  <!--   toc_float: true -->
  <!--   theme: spacelab -->


<!-- From https://stackoverflow.com/questions/45017632/getting-rmarkdown-command-line-arguments-printed-to-the-html-report -->


```{r setup.n.args, include=FALSE}
knitr::opts_knit$set(echo=FALSE, out.width='1000px', dpi=200, fig.keep="all")

options(width = 1000)
options(knitr.table.format = "html")

args <- commandArgs(trailingOnly=T)
parseArgs <- function(x) strsplit(sub("^--", "", x), "=")
args.df <- as.data.frame(do.call("rbind", parseArgs(args)))
args.list <- as.list(as.character(args.df$V2))
names(args.list) <- args.df$V1

require("knitr")
knitr::opts_knit$set(root.dir = args.list$root_dir)

```

```{r wd, include=FALSE}
getwd()
args.list$root_dir
```

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo=TRUE)
library(tidyverse)
library(mongolite)
library(bupaR.IACSmod)
library(processmapR.IACSmod)
library(edeaR.IACSmod)
library(ggthemes)
library(DiagrammeR)

#db_version is not required 
db_version = ""


stroke_log_collection <- mongo(db = paste0("stroke_", db_version),
                               collection = "activity_log",
                               url = "mongodb://localhost" )

stroke_log_df <- stroke_log_collection$find()

stroke_log_df$event <- factor(stroke_log_df$event,
                              c("urgent_care_admission",
                                "urgent_care_first_attention",
                                "urgent_care_ct",
                                "urgent_care_fibrinolysis",
                                "urgent_care_observation_room",
                                "urgent_care_discharge",
                                "urgent_care_exit",
                                "hospital_admission",
                                "hospital_surgery",
                                "hospital_discharge",
                                "long_stay_hospital_admission",
                                "long_stay_hospital_surgery",
                                "long_stay_hospital_discharge"))

levels(stroke_log_df$event) <-
  c("ER Admission",
    "ER First Attention",
    "ER CT",
    "ER Fibrinolysis",
    "ER Observation Room",
    "ER Discharge",
    "ER Exit",
    "Hospital Admission",
    "Hospital Surgery",
    "Hospital Discharge",
    "Long-stay Hospital Admission",
    "Long-stay Hospital Surgery",
    "Long-stay Hospital Discharge")

hospital_ids <- paste0("Hospital_",
                       formatC(rank(sort(unique(c(stroke_log_df$urgent_care_hospital_id, stroke_log_df$hospital_id)))), width = 2, flag = 0))
names(hospital_ids) <- sort(unique(c(stroke_log_df$urgent_care_hospital_id, stroke_log_df$hospital_id)))

colnames(stroke_log_df)[colnames(stroke_log_df)=="event"] <- "Activity"

# Eventlog construction (https://www.bupar.net/creating_eventlogs.html#lack_of_transitional_lifecycle)

eventlog_stroke <-
  stroke_log_df %>% mutate(status = "complete",
                           activity_instance = 1:nrow(.)) %>%
  eventlog(case_id = "id",
           activity_id = "Activity",
           timestamp = "timestamp",
           resource_id = "resource",
           activity_instance_id = "activity_instance",
           lifecycle_id = "status")

# Coloring
qual_col_pals = ggthemes::calc_pal()
qual_col_pals(12) -> dotted_chart_palette
dotted_chart_palette = dotted_chart_palette[1:length(sort(unique(eventlog_stroke$Activity)))]
cols <- dotted_chart_palette
names(cols) <- sort(unique(eventlog_stroke$Activity))

stroke_type_df <- read.csv("data/stroke_codes.csv", sep = ";")

```

## Process discovery results {.tabset}

### Overall

#### Trace Explorer

List of traces that cover 95% of the total episode count in the event logs

```{r trace_explorer_all, echo=FALSE, warning=FALSE}

eventlog_stroke %>%
  trace_explorer(coverage = 0.95,
                 show_labels = F,
                 scale_fill = scale_color_manual(values = cols,
                                                 aesthetics = c("colour", "fill")))

```

#### Process map (Frequency)

Frequency process map of episodes that cover 95% of the total episode count in the event logs

```{r process_map_freq_all, echo=FALSE, warning=FALSE, fig.height=10}
eventlog_stroke %>%
  filter_trace_frequency(percentage = 0.95) %>%
  process_map(rankdir = "TB", render = F) -> process_map_freq

render_graph(process_map_freq)

```


#### Process map (Median times)

Throughtput (median) time process map of episodes that cover 95% of the total episode count in the event logs

```{r process_map_time_all, echo=FALSE, warning=FALSE, fig.height=10}
eventlog_stroke %>%
  filter_trace_frequency(percentage = 0.95) %>%
  process_map(rankdir = "TB", type = performance(FUN=median, units = "hours"))
```

#### Timeline

Timeline of all episodes (relative starting time)

```{r timeline_all, echo=FALSE, warning=FALSE, message = FALSE}

eventlog_stroke %>% 
  dotted_chart(x = "relative", y = "duration", units = "days", palette = cols)
```

### Ischaemic Strokes

```{r ischaemic_stroke_setup, echo=FALSE, warning=FALSE}
eventlog_stroke %>%
  group_by_case %>%
  mutate(main_hospital_diagnosis =
           gsub(pattern='\\.',
                replacement='',
                x=as.factor(hospital_diagnosis_code[which(!is.na(hospital_diagnosis_code))[1]]))) %>%
  filter(main_hospital_diagnosis %in% (stroke_type_df %>% filter(type == "I") %>% pull(clean_code))) %>%
  ungroup_eventlog -> eventlog_stroke_ischaemic
```

#### Trace Explorer

List of traces that cover 95% of the total ischaemic episode count in the event logs

```{r trace_explorer_ischaemic, echo=FALSE, warning=FALSE}

eventlog_stroke_ischaemic %>%
  trace_explorer(coverage = 0.95,
                 show_labels = F,
                 scale_fill = scale_color_manual(values = cols,
                                                 aesthetics = c("colour", "fill")))

```

#### Process map (Frequency)

Frequency process map of episodes that cover 95% of the total ischaemic episode count in the event logs

```{r process_map_freq_ischaemic, echo=FALSE, warning=FALSE, fig.height=10}
eventlog_stroke_ischaemic %>%
  filter_trace_frequency(percentage = 0.95) %>%
  process_map(rankdir = "TB")
```


#### Process map (Median times)

Throughtput (median) time process map of episodes that cover 95% of the total ischaemic episode count in the event logs

```{r process_map_time_ischaemic, echo=FALSE, warning=FALSE, fig.height=10}
eventlog_stroke_ischaemic %>%
  filter_trace_frequency(percentage = 0.95) %>%
  process_map(rankdir = "TB", type = performance(FUN=median, units = "hours"))
```

#### Timeline

Timeline of all ischaemic  episodes (relative starting time)

```{r timeline_ischaemic, echo=FALSE, warning=FALSE, message = FALSE}

eventlog_stroke_ischaemic %>%
  dotted_chart(x = "relative", y = "duration", units = "days", palette = cols)
```

### Hemorrhagic Strokes

```{r hemorrhagic_stroke_setup, echo=FALSE, warning=FALSE}
eventlog_stroke %>%
  group_by_case %>%
  mutate(main_hospital_diagnosis =
           gsub(pattern='\\.',
                replacement='',
                x=as.factor(hospital_diagnosis_code[which(!is.na(hospital_diagnosis_code))[1]]))) %>%
  filter(main_hospital_diagnosis %in% (stroke_type_df %>% filter(type %in% c("H", "H")) %>% pull(clean_code))) %>%
  ungroup_eventlog -> eventlog_stroke_hemorrhagic
```

#### Trace Explorer

List of traces that cover 95% of the total hemorrhagic episodes count in the event logs

```{r trace_explorer_hemorrhagic, echo=FALSE, warning=FALSE}

eventlog_stroke_hemorrhagic %>%
  trace_explorer(coverage = 0.95,
                 show_labels = F,
                 scale_fill = scale_color_manual(values = cols,
                                                 aesthetics = c("colour", "fill")))

```

#### Process map (Frequency)

Frequency process map of episodes that cover 95% of the total hemorrhagic episodes count in the event logs

```{r process_map_freq_hemorrhagic, echo=FALSE, warning=FALSE, fig.height=10}
eventlog_stroke_hemorrhagic %>%
  filter_trace_frequency(percentage = 0.95) %>%
  process_map(rankdir = "TB")
```


#### Process map (Median times)

Throughtput (median) time process map of episodes that cover 95% of the total hemorrhagic episodes count in the event logs

```{r process_map_time_hemorrhagic, echo=FALSE, warning=FALSE, fig.height=10}
eventlog_stroke_hemorrhagic %>%
  filter_trace_frequency(percentage = 0.95) %>%
  process_map(rankdir = "TB", type = performance(FUN=median, units = "hours"))
```

#### Timeline

Timeline of all hemorrhagic  episodes (relative starting time)

```{r timeline_hemorrhagic, echo=FALSE, warning=FALSE, message = FALSE}

eventlog_stroke_hemorrhagic %>%
  dotted_chart(x = "relative", y = "duration", units = "days", palette = cols)
```

### R Session Info

This information is for debug purposes only

```{r sessionInfo, echo=F}
sessionInfo()
```
